Computing volume via non-linear rectangular prisms

### 2019-08-07 Cav2D/article-template.tex
added most of the figures to the article

%\item[\biogpic{\includegraphics[width=84pt]{Herbert_Hoover.pdf}}Herbert Hoover] (hchoover@stanford.edu) entered Stanford University in 1891, after failing all of the entrance exams except mathematics.  He received his BS degree in geology in 1895, spent time as a mining engineer, then was appointed by his co-author to the U.S. Food Administration and the Supreme Economic Council, where he orchestrated the greatest famine relief efforts of all time.
%\end{biog}
%This is not to say that there  This is partly, because there is no simplistic geometric interpretation for fractional calculus.  
\noindent
Bonaventura Cavalieri was a mathematician who lived in the 17th century. He made numerous contributions to the fields of optics, astronomy and geometry. 
Cavalieri was a student of Galileo. He served as a professor of mathematics at the university of Bologna from 1629 until his death in 1647. 
Galileo held Cavalieri in high esteem as is evedent from the following extract of a reference letter Galileo wrote in which he recommended Cavalieri for the chair of mathematics at Bologna: ``\emph{few, perhaps none, from 
Archimedes onwards, have investigated so deeply and have entered so far into the science of geometry}''. In 1935, a moon crater, Cavalerius, was officially named after him to commemorate his achievements and to honor his memory (see Fig ) \cite{?}. Cavalieri's most notable achievement was the publication of his 
treatise, \emph{Geometria indivisibilibus}, in which he describes the precalculus method of indivisibles. The method of indivisibles can be attributed to the ancient Greeks,
in this case Democritus and Archimedes. The method is used to compute the area and the volume of complex planar figures and solids, respectively.
It works by finding a planar figure or a solid, whose area or volume can easily be computed, which is Cavalieri congruent to a planar figure or solid whose 
area or volume is unknown. Two planar figures or solids are Cavalieri congruent if they can be decomposed into the same set of parallel ``indivisibles''. An indivisible of 
a planar figure is any cord of the planar figure. An indivisible of a solid is any planar section of a solid. Two indivisibles are equal if they are of the same length or area.
It is Cavalieri's principle that assures us that two planar figures or solids that are composed of the same set of indivisibles have equal area or volume. Cavalieri's principle 
in $\mathbb{R}^3$ is stated below without proof:

@@

>>>>

%\item[\biogpic{\includegraphics[width=84pt]{Herbert_Hoover.pdf}}Herbert Hoover] (hchoover@stanford.edu) entered Stanford University in 1891, after failing all of the entrance exams except mathematics.  He received his BS degree in geology in 1895, spent time as a mining engineer, then was appointed by his co-author to the U.S. Food Administration and the Supreme Economic Council, where he orchestrated the greatest famine relief efforts of all time.
%\end{biog}
%This is not to say that there  This is partly, because there is no simplistic geometric interpretation for fractional calculus.  
\noindent
Bonaventura Cavalieri was a mathematician who lived in the 17th century. He made numerous contributions to the fields of optics, astronomy and geometry. 
Cavalieri was a student of Galileo. He served as a professor of mathematics at the university of Bologna from 1629 until his death in 1647. 
Galileo held Cavalieri in high esteem as is evedent from the following extract of a reference letter Galileo wrote in which he recommended Cavalieri for the chair of mathematics at Bologna: ``\emph{few, perhaps none, from 
Archimedes onwards, have investigated so deeply and have entered so far into the science of geometry}''. In 1935, a moon crater, Cavalerius, was officially named after him to commemorate his achievements and to honor his memory (see Fig ) \cite{?}. 
\begin{figure}[htb]
\centering
\includegraphics[width=0.4\textwidth]{crater.jpg}
\caption{xx}
\label{fig:crater}
\end{figure}
Cavalieri's most notable achievement was the publication of his 
treatise, \emph{Geometria indivisibilibus}, in which he describes the precalculus method of indivisibles. The method of indivisibles can be attributed to the ancient Greeks,
in this case Democritus and Archimedes. The method is used to compute the area and the volume of complex planar figures and solids, respectively.
It works by finding a planar figure or a solid, whose area or volume can easily be computed, which is Cavalieri congruent to a planar figure or solid whose 
area or volume is unknown. Two planar figures or solids are Cavalieri congruent if they can be decomposed into the same set of parallel ``indivisibles''. An indivisible of 
a planar figure is any cord of the planar figure. An indivisible of a solid is any planar section of a solid. Two indivisibles are equal if they are of the same length or area.
It is Cavalieri's principle that assures us that two planar figures or solids that are composed of the same set of indivisibles have equal area or volume. Cavalieri's principle 
in $\mathbb{R}^3$ is stated below without proof:

@@

\begin{figure}[htb]
\centering
\includegraphics[width=0.5\textwidth]{cav_principle.pdf}
\caption{xx}
\label{fig:cav_principle}
\end{figure}
